\begin{enumerate}
  \item X. Zhang, M. Liu, and Y. Zhao, “Design of angle detection system based on MPU6050,” in \textit{Proc. Int. Conf. Intelligent Transportation, Big Data \& Smart City}, Changsha, China, 2017, pp. 159–162.
  \item S. J. Park and S. Y. Lee, “Real-Time Motion Recognition Using an Accelerometer,” \textit{Sensors}, vol. 15, no. 1, pp. 135–148, 2015.
  \item P. Kumar, J. Verma, and S. Prasad, “Hand Data Glove: A Wearable Real-Time Device for Human-Computer Interaction,” \textit{Int. J. Adv. Sci. Technol.}, vol. 43, pp. 15–23, Jun. 2012.
  \item A. Khandual and A. Biswal, “IoT Based Smart Glove for Hand Gesture Recognition,” \textit{Int. J. Sci. Res. Comput. Sci. Eng. Inf. Technol.}, vol. 5, no. 2, pp. 384–389, Mar. 2019.
  \item M. Nasri et al., “Design and Implementation of a 3D Printed Hand Gesture Recognition System Using Arduino and Flex Sensors,” \textit{IEEE Access}, vol. 7, pp. 55371–55378, 2019.
  \item T. Baudel and M. Beaudouin-Lafon, “Charade: Remote Control of Objects Using Free-Hand Gestures,” \textit{Commun. ACM}, vol. 36, no. 7, pp. 28–35, 1993.
  \item Rautaray, S. S., \& Agrawal, A. (2013). Real-time hand gesture recognition system       for dynamic applications. International Journal of UbiComp, 4(3), 21–35.
  \item Chowdhury, S., \& Haque, A. (2013). Animatronic hand controller. 
  \item Kumar, P., Verma, J., \& Prasad, S. (2012). Hand data glove: A wearable real-time device for human-computer
  \item Sturman, D. J., \& Zeltzer, D. (1994). A survey of glove-based input. *IEEE Computer Graphics and Applications, 14*(1), 30-39.
  \item Huang, J. (2017). Design of angle detection system based on MPU6050. *Advances in Computer Science Research, 73*, 1-3.
\end{enumerate}