<<<<<<< HEAD


\begin{itemize}
    \item \textbf{Real-time Hand Motion Tracking:} \\
    The system will accurately track and measure hand movements using the MPU6050 sensor for orientation (±2° accuracy), flex sensors for finger bending (0° to 90° range), and tactile switches for touch detection. The combined sensor data will provide comprehensive hand position and gesture information with minimal latency (<100ms).

    \item \textbf{Virtual Hand Replication:} \\
    The tracked hand movements will be replicated in real-time on a 3D hand model in Unreal Engine. The virtual hand will accurately mirror all finger movements, hand rotations, and touch interactions with smooth articulation and natural movement visualization. The system will maintain a consistent frame rate above 30 FPS to ensure fluid motion reproduction.

    \item \textbf{Interactive Response System:} \\
    The system will provide immediate feedback through the virtual hand model, responding to user inputs with less than 50ms latency. This includes accurate finger bend representation (±5° accuracy), precise hand orientation tracking, and immediate response to touch inputs with over 95\% reliability. The communication system will maintain a stable 60 Hz update rate to ensure seamless interaction between the physical and virtual hands.
\end{itemize}
=======
\section{Expected Output}

 The project aims to develop an innovative interactive gesture-controlled gaming system that
 translates real-hand movements into precise in-game character actions. The primary output will
 be a custom-designed wearable interface integrating MPU sensors, and mechanical switches
 enabling accurate hand gesture detection. The system will facilitate real-time data transmission
 between hardware and gameengine, creating an immersive first-person gaming experience with
 minimal latency. Key deliverables include a responsive input mechanism, gesture recognition
 algorithm, and puzzle game prototype demonstrating seamless hardware-software interaction.
 The project seeks to achieve 90 percent gesture detection accuracy, showcasing potential ad
vancements in interactive gaming technologies through innovative human-computer interface
 design.
 
>>>>>>> eaa8724d639cf7f9859b7d880d85f834c80e2ac2
